Web applications and their user interfaces are constantly growing larger and more complex.
In addition, software testing and implementing the test automation are very important and growing tasks in modern software development.
Prioritizing test cases for test automation is also very important for cost reasons and for resource optimization.
Acceptance testing can be prioritized and implemented by thinking the role of end user, allowing you to focus on testing truly essential functions and features, and save resources required for implementing test automation.

This thesis focuses on the automation of acceptance testing and solving the related problem of prioritizing test cases.
The thesis consists of two parts, which are the acceptance testing system that allows automation of the acceptance testing, and the mathematical prioritization method for the test cases in acceptance testing.

Four research questions were prepared for the study, which were also identified as one of the objectives of the work.
The research questions were related to the utilization of the weighted graph in the prioritization of test automation, the discovering of variables affecting the prioritization, explaining the connection between acceptance testing test cases and the weighted graph, and the integration of weighted graph based prioritization and test automation.

The work resulted in an acceptance testing system for testing the functionality of web user interfaces, as well as a repeatable mathematical method for prioritizing acceptance testing test cases.
The resulting prioritization method is the most important outcome of the work, which will hopefully be of maximum benefit to those who might need it to solve the prioritization problem.